An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-11-04 appendix.tex
Add additional acronyms and convert remaining mistakes

\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
    the same mixing process as the original variables) by
    Assumption~\ref{a3}, and the moment and size conditions in that
    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
    \begin{equation}\label{eq:2}
      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
    \end{equation}
    where $W(\cdot)$ is a multivariate Gaussian process.

>>>>

\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item The process $x_{t-1} \ep_t$ is $L_2$-\ned\ of size $-1/2$ (on
    the same mixing process as the original variables) by
    Assumption~\ref{a3}, and the moment and size conditions in that
    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
    \begin{equation}\label{eq:2}
      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
    \end{equation}
    where $W(\cdot)$ is a multivariate Gaussian process.

### 2014-11-04 mixedwindow.tex
Add additional acronyms and convert remaining mistakes

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 NBER-NSF Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,%
\footnote{Exceptions are \citepos{StW:07}
  IMA(1,1) and UC-SV models of inflation.} %
but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.%
\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} %
A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an LM or Wald test, which depend on just the
restricted or unrestricted model respectively.

@@

\section{Theoretical results supporting the asympotically normal OOS statistic}
\label{sec:1}

@@

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{1,t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the OOS average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

@@

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's MDS
null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

Consider the following environment. There is a single linear
benchmark model of the target variable, $y_{t+1}$:
\begin{equation}\label{eq:1}
  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T+1
\end{equation}
where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
observed vector of predictors. The parameter $\beta$ is
estimated with OLS using a recursive window as described by
Equation~\eqref{eq:8}
and the period-$t$ forecast is given by
\begin{equation}\label{eq:3}
  \yh_{0,t+1} = x_t'\bh_t.
\end{equation}

@@

Finally, we define some notation for the \oos\ statistic. The
adjusted OOS loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
Also define $\btrue$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
The next assumption ensures that $\Sigma$ is positive definite.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
\end{asmp}

@@

Asymptotic normality of the OOS average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} directly.

@@

Null hypothesis: $y_{t+1} - x_t'\btrue$ is an MDS with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

@@

Define the MDS covariance estimator:
\begin{align*}
  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
\end{align*}

@@

\section{Monte Carlo Results}\label{sec:2}
This section presents Monte Carlo experiments demonstrating that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they study, but can
have substantially higher power when the \dgp\ has a structural
break.%
\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the MASS
  \citep[7.3-22]{VeR:02} package.} %

@@

\begin{table}[tb]
  \centering
  \input{tex/mc1}
  \caption{Size and power of the \oos\ tests in the simulations
    described by Section~\ref{sec:2}, at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[CW roll.] shows the fraction of simulations for
    which Clark and West's (2007) rolling-window statistic rejects;
    Pr[CW rec.] shows the fraction of simulations for which
    their recursive-window statistic rejects; and Pr[new] shows the fraction of
    simulations for which this paper's test rejects.}
\label{tab:mc1}
\end{table}

@@

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance. A
full treatment of this issue is beyond the scope of this paper,
however, it is straightforward to use Theorem~\ref{res:1} and
Lemma~\ref{lem:2} to derive an appropriate critical value as
in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
the MDS null hypothesis, the continuous mapping theorem implies that
$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \Sh
\hat D^{-1/2})$ distribution to generate a critical value for the
\emph{largest} individual test statistic under the null ---
\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
this critical value, none of the predictors are siginificant at
\bootsize\%.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here. Moreover, I need to
  explain why it's not a concern for these statistics in general.} %

>>>>

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,%
\footnote{Exceptions are \citepos{StW:07}
  \allcaps{IMA}(1,1) and \allcaps{UC}-\allcaps{SV} models of inflation.} %
but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.%
\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} %
A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an \lm\ or Wald test, which depend on just the
restricted or unrestricted model respectively.

@@

\section{Theoretical results supporting the asympotically normal \oos\ statistic}
\label{sec:1}

@@

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{1,t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

@@

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

Consider the following environment. There is a single linear
benchmark model of the target variable, $y_{t+1}$:
\begin{equation}\label{eq:1}
  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T+1
\end{equation}
where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
observed vector of predictors. The parameter $\beta$ is
estimated with \ols\ using a recursive window as described by
Equation~\eqref{eq:8}
and the period-$t$ forecast is given by
\begin{equation}\label{eq:3}
  \yh_{0,t+1} = x_t'\bh_t.
\end{equation}

@@

Finally, we define some notation for the \oos\ statistic. The
adjusted \oos\ loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
Also define $\btrue$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
The next assumption ensures that $\Sigma$ is positive definite.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
\end{asmp}

@@

Asymptotic normality of the \oos\ average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} directly.

@@

Null hypothesis: $y_{t+1} - x_t'\btrue$ is an \mds\ with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

@@

Define the \mds\ covariance estimator:
\begin{align*}
  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
\end{align*}

@@

\section{Monte Carlo Results}\label{sec:2}
This section presents Monte Carlo experiments demonstrating that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they study, but can
have substantially higher power when the \dgp\ has a structural
break.%
\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
  \citep[7.3-22]{VeR:02} package.} %

@@

\begin{table}[tb]
  \centering
  \input{tex/mc1}
  \caption{Size and power of the \oos\ tests in the simulations
    described by Section~\ref{sec:2}, at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
    which Clark and West's (2007) rolling-window statistic rejects;
    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
    their recursive-window statistic rejects; and Pr[new] shows the fraction of
    simulations for which this paper's test rejects.}
\label{tab:mc1}
\end{table}

@@

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance. A
full treatment of this issue is beyond the scope of this paper,
however, it is straightforward to use Theorem~\ref{res:1} and
Lemma~\ref{lem:2} to derive an appropriate critical value as
in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
the \mds\ null hypothesis, the continuous mapping theorem implies that
$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \Sh
\hat D^{-1/2})$ distribution to generate a critical value for the
\emph{largest} individual test statistic under the null ---
\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
this critical value, none of the predictors are siginificant at
\bootsize\%.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here. Moreover, I need to
  explain why it's not a concern for these statistics in general.} %
